---
title: "Production_Planning_of_Wine-Northern_Napa_Valley_Winery_Inc."
output: github_document
---

*Importing Packages*
**Sales Data**
```{r message=FALSE, warning=FALSE}
library(car)
library(dplyr)
library(tidyverse)
library(psych)
library(caret)
library(fpp2)
library(forecast)
library(DescTools)
library(lubridate)
library(knitr)
library(rmarkdown)
library(readxl)

data <- read_excel("data.xlsx")
plot(data)
```

*I chose data from October 2000 for two reasons.*
*1) Grape harvest year starts from October to September.*
*2) Sales in December is much higher than any other month.* 
*So, I  considered sales of that month as an outlier and since outlier affects any forecasting model, I removed all other sales and started from Oct 2000  to get an accurate forecast.*


**linear Regression Model**

```{r}
model1 <- lm(Sales ~ Month, data = data)
summary(model1)
sales.lm <- predict(model1)
error <- data$Sales - sales.lm
rmse <- round(sqrt(mean(error^2)), digits = 2)
```

The RMSE for this model is `r rmse`.


**Moving Average Method**

```{r warning=FALSE}
data.ts <- ts(data$Sales, start = c(2000, 10), frequency = 12, names = "sales")
autoplot(data.ts, series = "Data") + autolayer(ma(data.ts,4), series = "3 Month MA") + autolayer(ma(data.ts,7), series = "6 Month MA") + autolayer(ma(data.ts, 5), series = "4 Month MA") + xlab("Month") + ylab("Sales")
```

*Moving average with span of 3,4, and 6 months*

```{r message=FALSE, warning=FALSE}
ma3 <- ma(data.ts, 4)
sales.ma3 <- forecast(ma3)
error.ma3 <- data.ts - sales.ma3$fitted
rsme.ma3 <- round(sqrt(mean(error.ma3^2)), digits = 2)

ma4 <- ma(data.ts, 5)
sales.ma4 <- forecast(ma4)
error.ma4 <- data.ts - sales.ma4$fitted
rsme.ma4 <- round(sqrt(mean(error.ma4^2)), digits = 2)

ma6 <- ma(data.ts, 7)
sales.ma6 <- forecast(ma6)
error.ma6 <- data.ts - sales.ma6$fitted
rsme.ma6 <- round(sqrt(mean(error.ma6^2)), digits = 2)
```

The RMSE for 3 month ma is `r rsme.ma3`, for 4 month ma is `r rsme.ma4`, and for 6 month ma is `r rsme.ma6`.

```{r warning=FALSE}
data.ts <- ts(data$Sales, start = c(2000, 10), frequency = 12, names = "sales")
autoplot(data.ts, main = "Wine Sales", xlab = "Year", ylab = "Sales (Cases of Wine)")
```

**Simple Exponential Smoothing Method**

```{r}
ses <- ses(data.ts, alpha = 0.399, h =13)
error.ses <- data.ts - ses$fitted
rmse.ses <- round(sqrt(mean(error.ses^2)), digits = 2)
x <- scales::percent(MAPE(ses$fitted, data.ts), accuracy = 0.01)
x1 <- MeanAD(ses$fitted)
x2 <- mean(error.ses^2)
plot(error.ses, ylab = "Residual")
summary(ses)
```

*Measure of Forecast Accuracy of Simple Exponential Smoothing Model*
AIC  = `r ses$aic`
RMSE = `r rmse.ses`
MAPE = `r x`
MAD  = `r x1`
MSE  = `r x2`


**Holt's Exponential Smoothing Method**

```{r}
h <- holt(data.ts, alpha= 0.314, h = 13)
error.h <- data.ts - h$fitted
rmse.h <- round(sqrt(mean(error.h^2)), digits = 2)
y <- scales::percent(MAPE(h$fitted, data.ts), accuracy = 0.01)
y1 <- MeanAD(h$fitted)
y2 <- mean(error.h^2)
plot(error.h, ylab = "Residual")
summary(h)
```

*Measure of Forecast Accuracy of Holt's Exponential Smoothing Model*
AIC  = `r h$aic`
RMSE = `r rmse.h`
MAPE = `r y`
MAD  = `r y1`
MSE  = `r y2`


**Holt Winter Exponential Smoothing Method**

```{r}
hw <- ets(data.ts, alpha = 0.282, beta = 0.001, gamma = 0.001)
sales.hw <- forecast(hw, h=13)
error.hw <- data.ts - sales.hw$fitted
rmse.hw <- round(sqrt(mean(error.hw^2)), digits = 2)
z <- scales::percent(MAPE(sales.hw$fitted, data.ts), accuracy = 0.01)
z1 <- MeanAD(sales.hw$fitted)
z2 <- mean(error.hw^2)
plot(error.hw, ylab = "Residual")
summary(hw)
sales.hw$mean
```

*Measure of Forecast Accuracy of Holt Winter Exponential Smoothing Model*
AIC  = `r hw$aic`
RMSE = `r rmse.hw`
MAPE = `r z`
MAD  = `r z1`
MSE  = `r z2`


**Building model with optimized parameter with ets**

```{r}
ets <- ets(data.ts)
sales.ets <- forecast(ets, h=13)
error.ets <- data.ts - sales.ets$fitted
rmse.ets <- round(sqrt(mean(error.ets^2)), digits = 2)
w <- scales::percent(MAPE(sales.ets$fitted, data.ts), accuracy = 0.01)
w1 <- MeanAD(sales.ets$fitted)
w2 <- mean(error.ets^2)
plot(error.ets, ylab = "Residual")
ets
```

*Measure of Forecast Accuracy of Optimized Exponential Smoothing Model*
AIC  = `r ets$aic`
RMSE = `r rmse.ets`
MAPE = `r w`
MAD  = `r w1`
MSE  = `r w2`


```{r}
#Data Frame of Chosen Model
hw.dataframe <- data.frame(sales.hw$mean)
sum(hw.dataframe[2:13, ])

#Question 6 (240000 cases - forecast cases)*price per case ($100)
sum(hw.dataframe[2:13, ])
juice.sell <- 240000 - sum(hw.dataframe[2:13, ])
juice.sell

#Economic Impact ($100) per case.
juice.sell*100
```
